### 2014-08-31 LaTeX/RhodiumIntro.tex
Tweaks in progress to intro and theory.

There are also puzzling cases of countries enmeshed in civil armed conflict that have seemingly little impact on economic growth. Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time. Yet, even as fatalities due to the drug war reached new peaks, Vikram Pandit of Citigroup cited Mexico in 2012 as being extremely well poised for growth and others argued that Mexico was actually beginning to catch up to its regional rival, Brazil \citep{vardi:2012}. This contrasts greatly with the economic fortunes of other countries in the midst of civil war where the economies have plumetted.

>>>>

There are also puzzling cases of countries enmeshed in civil armed conflict that have seemingly little impact on economic growth. Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time. Yet, even as fatalities due to the drug war reached new peaks, Vikram Pandit of Citigroup cited Mexico in 2012 as being extremely well poised for growth and others argued that Mexico was actually beginning to catch up to its regional rival, Brazil \citep{vardi:2012}. This contrasts greatly with the economic fortunes of other countries in the midst of civil war where the economies have plumetted. \cite{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.''  ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''  Nevertheless, some countries appear to weather domestic conflict better than others.

### 2014-08-31 LaTeX/RhodiumTheory.tex
Tweaks in progress to intro and theory.

We suspect that substate factors will determine the economic impacts of civil conflict.  While lootable resources are often pointed to as sources of funding for rebel groups, these same resources are often critical to state economic performance.  The loss of safe access to these resources due to internal conflict should adversly affect a state's economy.  Companies that rely on the extraction of resources may find themselves unable to access those resources if armed conflict is proximately located to the resource sites.  Therefore, we expect state economic performance to be directly related to the distance from conflict zones to valuable resources.

Other resources are also valuable to a state's ability to conduct business.  In particular, citizens must be able and willing to participate in commerce.  When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.  Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.  For this same reason, violence near important transporation hubs such as airports and sea ports should threaten business.

Finally, the perception of violence near major cities and resource centers should negatively impact foreign investment.  Investors will react negatively to news that violence is occuring near major cities and resources.  Investment is generally contingent on the expectation of a stable labor base and, sometimes, reliable access to resources.  Conflicts that appear to threaten these, whether they do or not, should correspond to a decrease in foreign investment.\footnote{While we intend to test each of these hypotheses carefully, our project in its current form addresses only the second hypothesis - the effect of conflict distance from city centers on aggregate state economic performance.  Future iterations of this paper will also include tests of the remaining hypotheses using foreign investment, economic growth, and domestic investment as dependent variables.}

While these hypotheses may resemble those of \cite{imai:weinstein:2000}, ours differs in the hypothesized mechanism through which conflict affects economic performance.  While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.  Conflict area is only one possible proxy for overall destructiveness.  However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) those resources outlined above.  In fact, we feel measures of proximity rather than spread are more appropriate to test the hypothesis that conflict obstucts vital economic activity.

>>>>

We suspect that substate factors will determine the economic impacts of civil conflict.  In particular, citizens must be able and willing to participate in commerce.  When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.  Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.  For this same reason, violence near important transporation hubs such as airports and sea ports should threaten business.

While this hypothesis may resemble those of \cite{imai:weinstein:2000}, ours differs in the hypothesized mechanism through which conflict affects economic performance.  While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.  Conflict area is only one possible proxy for overall destructiveness.  However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) those resources outlined above.  In fact, we feel measures of proximity rather than spread are more appropriate to test the hypothesis that conflict obstucts vital economic activity.
